---
title: "Regressions & Chloride Loads"
author: "Linnea"
date: "1/4/2021"
output: word_document
---

```{r setup, include=FALSE, warning = FALSE}
library(tidyverse)
library(lubridate)
library(gt)
library(webshot)
library(data.table)
library(segmented)
library(readxl)
library(dataRetrieval)
library(zoo)
source("Functions/readcl.R")
source("Functions/join_datasets_cond.R")
source("Functions/join_datasets_chloride.R")
source("Functions/L_theme.R")

#CHLORIDE DATA####
labWIC <- readCL("WIC")
labYN <- readCL("YN")
labYI <- readCL("YI")
labYS <- readCL("YS")
labSW <- readCL("SW")
lab6MC <- readCL("6MC")
labDC <- readCL("DC")
labPBMS <- readCL("PBMS")
labPBSF <- readCL("PBSF")

#cond data
DC_cond_data <- read_rds("Data/HOBO_Loggers/DC/DC_cond_data.rds")
YN_cond_data <- read_rds("Data/HOBO_Loggers/YN/YN_cond_data.rds")
YI_cond_data <- read_rds("Data/HOBO_Loggers/YI/YI_cond_data.rds")
YS_cond_data <- read_rds("Data/HOBO_Loggers/YS/YS_cond_data.rds")
SMC_cond_data <- read_rds("Data/HOBO_Loggers/6MC/SMC_cond_data.rds")
PBMS_cond_data <- read_rds("Data/HOBO_Loggers/PBMS/PBMS_cond_data.rds")
PBSF_cond_data <- read_rds("Data/HOBO_Loggers/PBSF/PBSF_cond_data.rds")
WIC_cond_data <- read_rds("Data/HOBO_Loggers/WIC/WIC_cond_data.rds")
SW_cond_data <- read_rds("Data/HOBO_Loggers/SW/SW_cond_data.rds")


source("functions/discharge_ts.R")

#discharge data
format <- function(d) {
  d %>%
  rename(discharge = X_00060_00000,
         date = dateTime) %>%
  select(date, discharge) %>%
  mutate(discharge = discharge * 0.028316847)
}

d.DC <- readNWISuv("05427930", "00060", "2019-12-01", "", tz = "GMT") %>%
  format()
DC_discharge <- rolling_ave_discharge(DC_cond_data, d.DC)

d.PBMS <- readNWISuv("05427948", "00060", "2019-12-01", "", tz = "GMT") %>%
  format()
PBMS_discharge <- rolling_ave_discharge(PBMS_cond_data, d.PBMS)

source("Functions/linreg.R")
source("regression_stats.R")
source("testing.R")

```


I am trying out segmented linear regressions using the segmented package (which picks the natural breaking point). I tried breaking up the regressions by salting vs. non-salting seasons (Oct-April and May-September) and that only slightly improved the relationships. 


Simple Linear Regression Plots
```{r regressionPlots, include=FALSE, warning = FALSE}

YN <- linreg(labYN, YN_cond_data) + labs(title = "Yahara North")
YI <- linreg(labYI, YI_cond_data) + labs(title = "Yahara Isthmus")
YS <- linreg(labYS, YS_cond_data) + labs(title = "Yahara South")
SMC <- linreg(lab6MC, SMC_cond_data) + labs(title = "Sixmile Creek")
DC <- linreg(labDC, DC_cond_data) + labs(title = "Dorn Creek")
PBMS <- linreg(labPBMS, PBMS_cond_data) + labs(title = "Pheasant Branch Creek - Main")
PBSF <- linreg(labPBSF, PBSF_cond_data) + labs(title = "Pheasant Branch Creek - South")
SW <- linreg(labSW, SW_cond_data) + labs(title = "Stakweather Creek")
WIC <- linreg(labWIC, WIC_cond_data) + labs(title = "Wingra Creek")



```

```{r, warning = F, message = F, echo = FALSE, fig.width = 7, fig.height = 4}
YN
SMC
DC
PBMS
PBSF
YI
WIC
SW
YS

simpleregtable

```

Segmented Linear Regression Plots
```{r seg.regressionPlots, include=FALSE, warning = FALSE}

YN_sg <- seglinreg(labYN, YN_cond_data) + labs(title = "Yahara North")
YI_sg <- seglinreg(labYI, YI_cond_data) + labs(title = "Yahara Isthmus")
YS_sg <- seglinreg(labYS, YS_cond_data) + labs(title = "Yahara South")
SMC_sg <- seglinreg(lab6MC, SMC_cond_data) + labs(title = "Sixmile Creek")
DC_sg <- seglinreg(labDC, DC_cond_data) + labs(title = "Dorn Creek")
PBMS_sg <- seglinreg(labPBMS, PBMS_cond_data) + labs(title = "Pheasant Branch Creek - Main")
PBSF_sg <- seglinreg(labPBSF, PBSF_cond_data) + labs(title = "Pheasant Branch Creek - South")
SW_sg <- seglinreg(labSW, SW_cond_data) + labs(title = "Stakweather Creek")
WIC_sg <- seglinreg(labWIC, WIC_cond_data) + labs(title = "Wingra Creek")

```

```{r, warning = F, message = F, echo = FALSE, fig.width = 7, fig.height = 4}
YN_sg
SMC_sg
DC_sg
PBMS_sg
PBSF_sg
YI_sg
WIC_sg
SW_sg
YS_sg

segmented_tbl

#Some of the regression lines seem a little funky, but the R^2 values are so much better. 

```

Here are a couple examples of chloride concentration and daily mass loading using the two methods. 

First is the Pheasant Branch Main Stem. The simple linear regression was good (0.86) and segmented was better (0.95). There does not seem to be a dramatic difference and using the segmented regression helps to eliminate the chloride concentrations/loads that are negative because of the intercept value. 

```{r, warning = F, message = F, echo = FALSE, fig.width = 7, fig.height = 4}
#Using simple linear regression
PBMS_example1
PBMS_example2

#Using segmented linear regression
PBMS_example3
PBMS_example4

```

These figures made with Dorn Creek data are a bit weirder. And maybe the lesson of this is I just can't predict chloride from specific conductivity in rivers with poor correlation. The simple linear regression was bad (0.33) and the segmented linear regression improved the correlation by nearly double (0.61). 

```{r, warning = F, message = F, echo = FALSE, fig.width = 7, fig.height = 4}
#Using simple linear regression
DC_example1
DC_example2

#Using segmented linear regression
DC_example3
DC_example4

```

